The effect of linking assumptions and number of response options on inferred scalar implicature rate

### 2018-05-09 writeup.Rmd
added brandons comments

The most prominently studied phenomenon in experimental pragmatics is undoubtedly *scalar implicature*. Scalar implicatures arise in virtue of **bw: as a result of?** a speaker producing the weaker of two ordered scalemates [@grice1975; @Horn1972; @Hirschberg1985; @Geurts2010]. Examples are provided in (1-2).

@@

A standard measure that has stood proxy **bw: stood as a proxy** for implicature rate across many studies is the proportion of 'pragmatic' judgments in truth-value judgment paradigms [@Bott2004;@Noveck2001;@Noveck2003;@Chemla2011;@Geurts2009;@DegenTanenhaus2015;@DeNeys2007;@Degen2014]. In these kinds of tasks, participants are provided a set of facts, either presented visually or via their own knowledge of the world. They are then asked to judge whether a sentence intended to describe those facts is true or false (or alternatively, whether it is right or wrong, or they are asked whether they agree or disagree with the sentence). The crucial condition for assessing implicature rates in these kinds of studies typically consists of a case where the facts are such that the stronger alternative is true and the target utterance is thus also true but underinformative. For instance, @Bott2004 asked participants to judge sentences like 'Some elephants are mammals', when world knowledge dictates that all elephants are mammals. Similarly, @DegenTanenhaus2015 asked participants to judge sentences like 'You got some of the gumballs' in situations where the visual evidence indicated that the participant received all the gumballs from a gumball machine. In these kinds of scenarios, the story goes, if a participant responds 'FALSE', that indicates that they computed a scalar implicature, eg to the effect of 'Not all elephants are mammals' or 'You didn't get all of the gumballs', which is (globally or contextually) false. If instead a participant responds 'TRUE', that is taken to indicate that they interpreted the utterance literally as `Some, and possibly all, elephants are mammals' or 'You got some, and possibly all, of the gumballs'.

@@

We begin by reporting an experiment that addresses the following question: do the number of response options provided in a truth-value judgment task and the way that responses are grouped into pragmatic ('SI') and literal ('no SI') change inferences about scalar implicature rates? Note that this way of asking the question presupposes two things: first, that whatever participants are doing in a truth-value judgment task, the behavioral measure can be interpreted as providing a measure of *interpretation*. And second, **bw: change to semicolon, i.e. "... interpretation; and second,**  that listeners either do or do not compute an implicature on any given occasion. In the General Discussion we will discuss both of these issues. First, following @Degen2014, we will offer some remarks on why truth-value judgment tasks are better thought of as measuring participants' estimates of speakers' *production* probabilities. This will suggest a completely different class of linking functions. And second, **bw: Next, (to avoid redundancy -- see above)** we discuss an alternative conception of scalar implicature as a probabilistic phenomeonen, a view that has recently rose to prominence in the subfield of probabilistic pragmatics [@Franke2016;@Goodman2016]. This alternative conception of scalar implicature, we argue, affords developing and testing quantitative linking functions in a rigorous and motivated way.

@@

```{r linkvisualization, fig.asp=0.2,fig.cap = "Strong and weak link from response options to researcher inference about scalar implicature rate, exemplified for the disjunctive utterance when the conjunction is true."}
link_img <- png::readPNG("writeup_files/figures/link-visualization.png")
grid::grid.raster(link_img)
```

Let's examine an example. Assume three response options (wrong, neither, right). Assume further that a third of participants each gave each of the three responses, **bw: Assume further that each of the three responses was selected by a third of participants,** i.e., the distributions of responses is 1/3, 1/3, and 1/3. Under the Strong link, we infer that this task yielded an implicature rate of 2/3. Under the Weak link, we infer that this task yielded an implicature rate of 1/3. This is quite a drastic difference if we are for instance **bw: if we are, for instance, **interested in whether scalar implicatures are inference defaults and we would like to interpret an implicature rate of above an arbitrary threshold (e.g., 50%) as evidence for such a claim. Under the Strong link, we would conclude that scalar implicatures are not defaults. Under the Weak link, we would conclude that they are. In the experiment reported in the following section, we presented participants with exactly this setup. We manipulated the number of response options between participants and analyzed the results under different linking assumptions.

@@

Participants played an online card game in which they were asked to judge descriptions of the contents of cards. Different groups of participants were presented with different numbers of response options. On critical trials, participants were presented with descriptions for the cards that typically result in exhaustivity implicatures ("There is a cat on the card" when there was a cat and a dog) or scalar implicatures ("There is a cat or a dog on the card" when there was a cat and a dog). We categorized their responses on such trials according to the weak and the strong link introduced above, and tested whether the number of response options and the linking assumptions led to different conclusions about the rate of computed implicatures in the experimental task.

@@

In the binary task, participants were at or close to ceiling in responding 'right' and 'wrong' on unambiguously true and false trials, respectively (see Figure \@ref(fig:binaryPlot)). However, on underinformative trials ("cat" and "cat or dog" description for card with cat and dog), we observe pragmatic behavior: on exhaustive trials, participants judged the utterance "wrong" `r round(binaryExh_wrong$proportion*100)`% of the time;  on scalar trials, participants judged the utterance "wrong" `r round(binaryScalar_wrong$proportion*100)`% of the time. That is, both under the weak and the strong link assumptions introduced in the Introduction, inferred implicature rate on exhaustive trials is `r round(binaryExh_wrong$proportion*100)`% and on scalar trials `r round(binaryScalar_wrong$proportion*100)`%.

@@

In the ternary task, participants were also at or close to ceiling in responding 'right' and 'wrong' on unambiguously true and false trials, respectively (see Figure \@ref(fig:ternaryPlot)). And again, on underinformative trials ("cat" and "cat or dog" description for card with cat and dog), we observed pragmatic behavior: on exhaustive trials, participants considered the guess "wrong" `r round(ternaryExh_wrong$proportion*100)`% of the time and neither wrong nor right `r round(ternaryExh_neither$proportion*100)`% of the time. On scalar trials, participants judged the guess "wrong" `r round(ternaryScalar_wrong$proportion*100)`% of the time and "neither" `r round(ternaryScalar_neither$proportion*100)`% of the time. This means that the weak and strong link lead to different conclusions about implicature rates on the ternary task. Under the weak link, inferred implicature rate on exhaustive trials is `r round(ternaryExh_wrong$proportion*100) + round(ternaryExh_neither$proportion*100)`%; under the strong link it is only `r round(ternaryExh_wrong$proportion*100)`%. Similarly, under the weak link, inferred implicature rate on scalar trials is `r round(ternaryScalar_wrong$proportion*100) + round(ternaryScalar_neither$proportion*100)`%; under the strong link it is only `r round(ternaryScalar_wrong$proportion*100)`%.

@@

In the quaternary task (Figure \@ref(fig:quaternaryPlot)), participants were again at or close to ceiling in responding 'right' and 'wrong' on 4 of the 6 unambiguously true and false trials. However, with four response options, two of the control conditions appear to be showing signs of pragmatic infelicity: when a conjunction was used and only one of the animals was on the card, participants considered the guess "wrong" most of the time, but they often considered it "kinda wrong" or even "kinda right". This suggests that perhaps participants considered a notion of partially true or correct statement in our experimental setting. Disjunctive descriptions of cards with only one animal, while previously at ceiling for "right" responses, were downgraded to only "kinda right" 26% of the time, presumably because these utterances are also underinformative, though the degree of underinformativeness may be less egregious than on scalar trials.

@@

Thus, we are again forced to draw different conclusions about implicature rates depending on whether we assume the weak link or the strong link. Under the weak link, inferred implicature rate on exhaustive trials is `r round(quaternaryExh_wrong$proportion*100) + round(quaternaryExh_kindaWrong$proportion*100) + round(quaternaryExh_kindaRight$proportion*100)`%; under the strong link it is only `r round(quaternaryExh_wrong$proportion*100)`%. Similarly, under the weak link, inferred implicature rate on scalar trials is `r round(quaternaryScalar_wrong$proportion*100) + round(quaternaryScalar_kindaWrong$proportion*100) + round(quaternaryScalar_kindaRight$proportion*100)`%; under the strong link it is only `r round(quaternaryScalar_wrong$proportion*100)`%.

@@

Finally, Figure \@ref(fig:quinaryPlot) shows the proportion of  responses in the quinary task. Performance on the 4 pragmatically felicitous control trials was again at floor and ceiling, respectively. The 2 control conditions that the quaternary task had revealed pragmatic infelicity in again displayed that pragmatic infelicity in the quinary task, suggesting that this is a robust type of pragmatic infelicity that, however, requires fine-grained enough response options to be detected experimentally.

@@

Thus, we would again draw different conclusions about implicature rates depending on whether we assume the weak link or the strong link. Under the weak link, inferred implicature rate on exhaustive trials is `r round(quinaryExh_wrong$proportion*100) + round(quinaryExh_kindaWrong$proportion*100) + round(quinaryExh_Neither$proportion*100) + round(quinaryExh_kindaRight$proportion*100)`%; under the strong link it is only `r round(quinaryExh_wrong$proportion*100)`%. Similarly, under the weak link, inferred implicature rate on scalar trials is `r round(quinaryScalar_wrong$proportion*100) + round(quinaryScalar_kindaWrong$proportion*100) + round(quinaryScalar_Neither$proportion*100) + round(quinaryScalar_kindaRight$proportion*100)`%; under the strong link it is only `r round(quinaryScalar_wrong$proportion*100)`%.

<!--
In four trial types, participants provided the same responses regardless of how many response options were made available. The first two trial types include the guesses with an animal not on the card at all. In such trials, whether there was one or two animals on the card, participants considered the guess wrong. In the third and the fourth trial types, the gueses matched the aimal(s) on the card; if there was one animal on the card, that animal was mentioned and if there were two, both were mentioned using a conjunction. The fact that participants chose the extreme ends of the scale for these trial types and the responses did not change when intermediate options were provided suggests that participant judgments truly aligned with the opposite ends of the scale in these trial types.

@@

Our primary goal in this study was to test whether the estimated implicature rate in the experimental task is affected by the linking assumption and the number of response options available to participants. To this end, we only analyzed the critical trials (exhaustive and scalar). In particular, we classified each data point from critical trials as constituting an implicature (1) or not (0) under the strong and weak link. Figure \@ref(fig:implicatureRatePlot) shows the resulting implicature rates by condition and link.

Visually, the weak link tends to result in greater estimates of implicature rates, especially in tasks with more response options. Under the strong link, this latter pattern is reversed: the binary and ternary judgment tasks result in greater estimates of implicature rates than with more response options.

@@

The model provided evidence for the following effects: First, there was a main effect of trial type such that scalar trials resulted in greater implicature rates than exhaustive trials (Mean Estimate = `r round(fixed_effects$Estimate[6],2)`, 95% Credible Interval=[`r round(fixed_effects$X2.5.ile[6],2)`, `r round(fixed_effects$X97.5.ile[6],2)`]). Second, there was an interaction between link and number of response options such that the quaternary task (Mean Estimate = `r round(fixed_effects$Estimate[7],2)`, 95% Credible Interval=[`r round(fixed_effects$X2.5.ile[7],2)`, `r round(fixed_effects$X97.5.ile[7],2)`]) and the quinary task  (Mean Estimate = `r round(fixed_effects$Estimate[8],2)`, 95% Credible Interval=[`r round(fixed_effects$X2.5.ile[8],2)`, `r round(fixed_effects$X97.5.ile[8],2)`]) with a weak link resulted in greater implicature rates. Finally, there was a three-way interaction between link, trial type, and number of response options (Mean Estimate = `r round(fixed_effects$Estimate[15],2)`, 95% Credible Interval=[`r round(fixed_effects$X2.5.ile[15],2)`, `r round(fixed_effects$X97.5.ile[15],2)`]). One interpretation of this interaction is that the difference between the weak and strong link on scalar trials in the quinary task was smaller than on exhaustive trials, though we believe this is not too interesting, given that the binary reference level implicature estimate was lower for exhaustive trials in the first place. **JD: happy to throw out this last sentence** Crucially, both number of response options and link affect the inferred implicature rate.

@@

We asked whether the linking assumptions and the number of response options available to participants affects the inferred implicature rate in an experimental study. The results presented here suggest they do. A linking assupmtion that considered the highest point on the scale as literal and any lower point as pragmatic (weak link) resulted in higher implicature rates in tasks with 4 or 5 response options. A linking assumption that considered the lowest point on the scale as pragmatic and any higher point as literal (strong link) reported lower implicature rates in tasks with 4 or 5 options. The results suggest that the choice of linking assumption is a crucial analytical step that can significantly impact the conclusions drawn from truth value judgment tasks. In particular, there is danger for pragmatic ability to be both under- and overestimated.

While the binary truth value judgement task avoids the analytic decision between strong and weak linking assumptions, the results reported here suggest that binary tasks can also underestimate participants' pragmatic competence. In binary tasks, participants are often given the lowest and highest points on a scale ("wrong" vs. "right") and are asked to report pragmatic infelicities using the lowest point (e.g. "wrong"). The study reported here showed that on trials with true but pragmatically infelicitous descriptions, participants often avoided the lowest point on the scale if they were given more intermediate options. Even though the option "wrong" was available to participants in all tasks, participants in tasks with intermediate options chose it less often. In computing implicature rate, this pattern manifested itself as a decrease in implicature rate under the strong link when more response options were provided, and an increase in implicature rate under the weak link when more response options were provided. These conclusions are in line with @Katsos2011's argument that pragmatic violations are not as severe as semantic violations and participants do not penalize them as much. Providing participants with only the extreme ends of the scale (e.g. wrong/right, false/true) when pragmatic violations are considered to be of an intermediate nature risks misrepresentation of participants' pragmatic competence. It further suggests that in studies that use binary tasks to investigate response-contingent processing, proportions of "literal" responses may be a composite of both literal and pragmatic underlying interpretations that just happen to get mapped differently onto different response options by participants.

>>>>

The most prominently studied phenomenon in experimental pragmatics is undoubtedly *scalar implicature*. Scalar implicatures arise as a result of a speaker producing the weaker of two ordered scalemates [@grice1975; @Horn1972; @Hirschberg1985; @Geurts2010]. Examples are provided in (1-2).

@@

A standard measure that has stood as a proxy for implicature rate across many studies is the proportion of 'pragmatic' judgments in truth-value judgment paradigms [@Bott2004;@Noveck2001;@Noveck2003;@Chemla2011;@Geurts2009;@DegenTanenhaus2015;@DeNeys2007;@Degen2014]. In these kinds of tasks, participants are provided a set of facts, either presented visually or via their own knowledge of the world. They are then asked to judge whether a sentence intended to describe those facts is true or false (or alternatively, whether it is right or wrong, or they are asked whether they agree or disagree with the sentence). The crucial condition for assessing implicature rates in these kinds of studies typically consists of a case where the facts are such that the stronger alternative is true and the target utterance is thus also true but underinformative. For instance, @Bott2004 asked participants to judge sentences like 'Some elephants are mammals', when world knowledge dictates that all elephants are mammals. Similarly, @DegenTanenhaus2015 asked participants to judge sentences like 'You got some of the gumballs' in situations where the visual evidence indicated that the participant received all the gumballs from a gumball machine. In these kinds of scenarios, the story goes, if a participant responds 'FALSE', that indicates that they computed a scalar implicature, eg to the effect of 'Not all elephants are mammals' or 'You didn't get all of the gumballs', which is (globally or contextually) false. If instead a participant responds 'TRUE', that is taken to indicate that they interpreted the utterance literally as `Some, and possibly all, elephants are mammals' or 'You got some, and possibly all, of the gumballs'.

@@

We begin by reporting an experiment that addresses the following question: do the number of response options provided in a truth-value judgment task and the way that responses are grouped into pragmatic ('SI') and literal ('no SI') change inferences about scalar implicature rates? Note that this way of asking the question presupposes two things: first, that whatever participants are doing in a truth-value judgment task, the behavioral measure can be interpreted as providing a measure of interpretation; and second,  that listeners either do or do not compute an implicature on any given occasion. In the General Discussion we will discuss both of these issues. First, following @Degen2014, we will offer some remarks on why truth-value judgment tasks are better thought of as measuring participants' estimates of speakers' *production* probabilities. This will suggest a completely different class of linking functions. Next, we discuss an alternative conception of scalar implicature as a probabilistic phenomeonen, a view that has recently rose to prominence in the subfield of probabilistic pragmatics [@Franke2016;@Goodman2016]. This alternative conception of scalar implicature, we argue, affords developing and testing quantitative linking functions in a rigorous and motivated way.

@@

```{r linkvisualization, fig.asp=0.2,fig.cap = "Strong and Weak link from response options to researcher inference about scalar implicature rate, exemplified for the disjunctive utterance when the conjunction is true."}
link_img <- png::readPNG("writeup_files/figures/link-visualization.png")
grid::grid.raster(link_img)
```

Let's examine an example. Assume three response options (wrong, neither, right).  Assume further that each of the three responses was selected by a third of participants, i.e., the distributions of responses is 1/3, 1/3, and 1/3. Under the Strong link, we infer that this task yielded an implicature rate of 2/3. Under the Weak link, we infer that this task yielded an implicature rate of 1/3. This is quite a drastic difference if we are, for instance, interested in whether scalar implicatures are inference defaults and we would like to interpret an implicature rate of above an arbitrary threshold (e.g., 50%) as evidence for such a claim. Under the Strong link, we would conclude that scalar implicatures are not defaults. Under the Weak link, we would conclude that they are. In the experiment reported in the following section, we presented participants with exactly this setup. We manipulated the number of response options between participants and analyzed the results under different linking assumptions.

@@

Participants played an online card game in which they were asked to judge descriptions of the contents of cards. Different groups of participants were presented with different numbers of response options. On critical trials, participants were presented with descriptions for the cards that typically result in exhaustivity implicatures ("There is a cat on the card" when there was a cat and a dog) or scalar implicatures ("There is a cat or a dog on the card" when there was a cat and a dog). We categorized their responses on such trials according to the weak and the Strong link introduced above, and tested whether the number of response options and the linking assumptions led to different conclusions about the rate of computed implicatures in the experimental task.

@@

In the binary task, participants were at or close to ceiling in responding 'right' and 'wrong' on unambiguously true and false trials, respectively (see Figure \@ref(fig:binaryPlot)). However, on underinformative trials (i.e. a "cat" or "cat or dog" description for a card with both a cat and a dog), we observe pragmatic behavior: on exhaustive trials, participants judged the utterance "wrong" `r round(binaryExh_wrong$proportion*100)`% of the time;  on scalar trials, participants judged the utterance "wrong" `r round(binaryScalar_wrong$proportion*100)`% of the time. That is, both under the Weak and Strong link assumptions introduced in the Introduction, inferred implicature rate on exhaustive trials is `r round(binaryExh_wrong$proportion*100)`% and on scalar trials `r round(binaryScalar_wrong$proportion*100)`%.

@@

In the ternary task, participants were also at or close to ceiling in responding 'right' and 'wrong' on unambiguously true and false trials, respectively (see Figure \@ref(fig:ternaryPlot)). And again, on underinformative trials (a "cat" and "cat or dog" description for a card with both a cat and a dog), we observed pragmatic behavior: on exhaustive trials, participants considered the guess "wrong" `r round(ternaryExh_wrong$proportion*100)`% of the time and neither wrong nor right `r round(ternaryExh_neither$proportion*100)`% of the time. On scalar trials, participants judged the guess "wrong" `r round(ternaryScalar_wrong$proportion*100)`% of the time and "neither" `r round(ternaryScalar_neither$proportion*100)`% of the time. This means that the Weak and Strong link lead to different conclusions about implicature rates on the ternary task. Under the Weak link, inferred implicature rate on exhaustive trials is `r round(ternaryExh_wrong$proportion*100) + round(ternaryExh_neither$proportion*100)`%; under the Strong link it is only `r round(ternaryExh_wrong$proportion*100)`%. Similarly, under the Weak link, inferred implicature rate on scalar trials is `r round(ternaryScalar_wrong$proportion*100) + round(ternaryScalar_neither$proportion*100)`%; under the Strong link it is only `r round(ternaryScalar_wrong$proportion*100)`%.

@@

In the quaternary task (Figure \@ref(fig:quaternaryPlot)), participants were again at or close to ceiling in responding 'right' and 'wrong' on 4 of the 6 unambiguously true and false trials. However, with four response options, two of the control conditions appear to be showing signs of pragmatic infelicity: when a conjunction was used and only one of the animals was on the card, participants considered the guess "wrong" most of the time, but they often considered it "kinda wrong" or even "kinda right". This suggests that perhaps participants considered the notion of a partially true or correct statement in our experimental setting. Disjunctive descriptions of cards with only one animal, while previously at ceiling for "right" responses, were downgraded to only "kinda right" 26% of the time, presumably because these utterances are also underinformative, though the degree of underinformativeness may be less egregious than on scalar trials.

@@

Thus, we are again forced to draw different conclusions about implicature rates depending on whether we assume the Weak link or the Strong link. Under the Weak link, inferred implicature rate on exhaustive trials is `r round(quaternaryExh_wrong$proportion*100) + round(quaternaryExh_kindaWrong$proportion*100) + round(quaternaryExh_kindaRight$proportion*100)`%; under the Strong link it is only `r round(quaternaryExh_wrong$proportion*100)`%. Similarly, under the Weak link, inferred implicature rate on scalar trials is `r round(quaternaryScalar_wrong$proportion*100) + round(quaternaryScalar_kindaWrong$proportion*100) + round(quaternaryScalar_kindaRight$proportion*100)`%; under the Strong link it is only `r round(quaternaryScalar_wrong$proportion*100)`%.

@@

Finally, Figure \@ref(fig:quinaryPlot) shows the proportion of responses in the quinary task. Performance on the 4 pragmatically felicitous control trials was again at floor and ceiling, respectively. The 2 control conditions in which the quaternary task had revealed pragmatic infelicity  again displayed that pragmatic infelicity in the quinary task, suggesting that this is a robust type of pragmatic infelicity that, nonetheless, requires fine-grained enough response options to be detected experimentally.

@@

Thus, we would again draw different conclusions about implicature rates depending on whether we assume the Weak link or the Strong link. Under the Weak link, inferred implicature rate on exhaustive trials is `r round(quinaryExh_wrong$proportion*100) + round(quinaryExh_kindaWrong$proportion*100) + round(quinaryExh_Neither$proportion*100) + round(quinaryExh_kindaRight$proportion*100)`%; under the Strong link it is only `r round(quinaryExh_wrong$proportion*100)`%. Similarly, under the Weak link, inferred implicature rate on scalar trials is `r round(quinaryScalar_wrong$proportion*100) + round(quinaryScalar_kindaWrong$proportion*100) + round(quinaryScalar_Neither$proportion*100) + round(quinaryScalar_kindaRight$proportion*100)`%; under the Strong link it is only `r round(quinaryScalar_wrong$proportion*100)`%. 
<!--
In four trial types, participants provided the same responses regardless of how many response options were made available. The first two trial types include the guesses with an animal not on the card at all. In such trials, whether there was one or two animals on the card, participants considered the guess wrong. In the third and the fourth trial types, the gueses matched the aimal(s) on the card; if there was one animal on the card, that animal was mentioned and if there were two, both were mentioned using a conjunction. The fact that participants chose the extreme ends of the scale for these trial types and the responses did not change when intermediate options were provided suggests that participant judgments truly aligned with the opposite ends of the scale in these trial types.

@@

Our primary goal in this study was to test whether the estimated implicature rate in the experimental task is affected by the linking assumption and the number of response options available to participants. To this end, we only analyzed the critical trials (exhaustive and scalar). In particular, we classified each data point from critical trials as constituting an implicature (1) or not (0) under the strong and Weak link. Figure \@ref(fig:implicatureRatePlot) shows the resulting implicature rates by condition and link.

Visually, the Weak link tends to result in greater estimates of implicature rates, especially in tasks with more response options. Under the Strong link, this latter pattern is reversed: the binary and ternary judgment tasks result in greater estimates of implicature rates than with more response options.

@@

The model provided evidence for the following effects: First, there was a main effect of trial type such that scalar trials resulted in greater implicature rates than exhaustive trials (Mean Estimate = `r round(fixed_effects$Estimate[6],2)`, 95% Credible Interval=[`r round(fixed_effects$X2.5.ile[6],2)`, `r round(fixed_effects$X97.5.ile[6],2)`]). Second, there was an interaction between link and number of response options such that the quaternary task (Mean Estimate = `r round(fixed_effects$Estimate[7],2)`, 95% Credible Interval=[`r round(fixed_effects$X2.5.ile[7],2)`, `r round(fixed_effects$X97.5.ile[7],2)`]) and the quinary task  (Mean Estimate = `r round(fixed_effects$Estimate[8],2)`, 95% Credible Interval=[`r round(fixed_effects$X2.5.ile[8],2)`, `r round(fixed_effects$X97.5.ile[8],2)`]) with a Weak link resulted in greater implicature rates. Finally, there was a three-way interaction between link, trial type, and number of response options (Mean Estimate = `r round(fixed_effects$Estimate[15],2)`, 95% Credible Interval=[`r round(fixed_effects$X2.5.ile[15],2)`, `r round(fixed_effects$X97.5.ile[15],2)`]). One interpretation of this interaction is that the difference between the weak and Strong link on scalar trials in the quinary task was smaller than on exhaustive trials, though we believe this is not too interesting, given that the binary reference level implicature estimate was lower for exhaustive trials in the first place. **JD: happy to throw out this last sentence** Crucially, both number of response options and link affect the inferred implicature rate.

@@

We asked whether the linking assumptions and the number of response options available to participants affects the inferred implicature rate in an experimental study. The results presented here suggest they do. A linking assupmtion that considered the highest point on the scale as literal and any lower point as pragmatic (Weak link) resulted in higher implicature rates in tasks with 4 or 5 response options. A linking assumption that considered the lowest point on the scale as pragmatic and any higher point as literal (Strong link) reported lower implicature rates in tasks with 4 or 5 options. The results suggest that the choice of linking assumption is a crucial analytical step that can significantly impact the conclusions drawn from truth value judgment tasks. In particular, there is danger for pragmatic ability to be both under- and overestimated.

While the binary truth value judgement task avoids the analytic decision between strong and Weak linking assumptions, the results reported here suggest that binary tasks can also underestimate participants' pragmatic competence. In binary tasks, participants are often given the lowest and highest points on a scale ("wrong" vs. "right") and are asked to report pragmatic infelicities using the lowest point (e.g. "wrong"). The study reported here showed that on trials with true but pragmatically infelicitous descriptions, participants often avoided the lowest point on the scale if they were given more intermediate options. Even though the option "wrong" was available to participants in all tasks, participants in tasks with intermediate options chose it less often. In computing implicature rate, this pattern manifested itself as a decrease in implicature rate under the Strong link when more response options were provided, and an increase in implicature rate under the Weak link when more response options were provided. These conclusions are in line with @Katsos2011's argument that pragmatic violations are not as severe as semantic violations and participants do not penalize them as much. Providing participants with only the extreme ends of the scale (e.g. wrong/right, false/true) when pragmatic violations are considered to be of an intermediate nature risks misrepresentation of participants' pragmatic competence. It further suggests that in studies that use binary tasks to investigate response-contingent processing, proportions of "literal" responses may be a composite of both literal and pragmatic underlying interpretations that just happen to get mapped differently onto different response options by participants.
